Type Refinements for the Working Class

### 2016-01-01 paper.tex
define necessity; add futher remark to independence (#13)

\begin{thm}
  The refinement operator $\Indep{-}{a}$ is an idempotent comonad on refinements
  in the sense that the following rules are valid:

@@

%% \subsubsection{Nominal Necessity}
%%
%% \subsubsection{Nominal Possibility}
%%
\section{Related Work}

>>>>

\begin{remark}
  Note that we could not have simply used
  $\RMemEq{\Upsilon'\setminus\rho(a)}{M}{N}{\phi}$ as the premise in our
  definition, since that would be outside the range of significance of this
  form of judgment (i.e.\ the presuppositions fail to be satisfied); in
  particular, it is not guaranteed that the refinement $\phi$ is defined at
  $\Upsilon'\setminus\rho(a)$, and nor do we have
  $\Member{M,N}{\Exprs_\tau(\Upsilon'\setminus\rho(a))}$.
\end{remark}

\begin{thm} \label{thm:independence-comonadic}
  The refinement operator $\Indep{-}{a}$ is an idempotent comonad on refinements
  in the sense that the following rules are valid:

@@

\subsubsection{Nominal Necessity}

Another comonadic refinement modality is \emph{nominal necessity}
$\HypJ{\Refines{\Upsilon}{\square\phi}{\tau}}{\Refines{\Upsilon}{\phi}{\tau}}$,
which expresses the independence of an object from \emph{any} atoms at all. For
any renaming
\begin{tikzcd}[cramped]
  \IMode{\Upsilon}\arrow[r,hook,"\IMode{\rho}"] &\IMode{\Upsilon'}
\end{tikzcd}%
, we define nominal necessity as follows:
\[
  \infer={
    \RMemEq{\Upsilon'}{M}{N}{\square\phi}
  }{
    \exists\Member{L}{\Exprs_\tau(\cdot)}.
    \begin{array}{l}
      \RMemEq{\Upsilon'}{L}{M}{\phi}\\
      \RMemEq{\Upsilon'}{L}{N}{\phi}
    \end{array}
  }
\]

\begin{thm}
  Nominal independence is an idempotent comonadic modality on refinements.
\end{thm}
\begin{proof}
  The demonstration is essentially analogous to the one for independence in
  Theorem~\ref{thm:independence-comonadic}.
\end{proof}

%% \subsubsection{Nominal Possibility}
%%
\section{Related Work}
